Fractional anisotropy as an optimal tracer of cosmic voids

### 2014-08-13 cosmic_voids.tex
Finishing T-web and V-web descriptions and reordering figures and tables

%-------------------------------------------------------------------------
\subsection{The tidal web (T-web)}
\label{subsec:Tweb}
%-------------------------------------------------------------------------

This scheme was initially proposed by \citet{Hahn07} as a novel 
alternative for classifying the Cosmic Web based upon the tidal tensor, 
that is somehow more fundamental than the density field as it also allows 
to quantify the orbital dynamics of the matter field. This approach is 
reached by a second-order expansion of the equations of motion around 
local minima of the gravitational potential and then extended to any 
position. The second-order term corresponds to the tidal tensor, which is 
defined as the Hessian of the normalized gravitational potential

%.........................................................................
%Tidal Tensor
\begin{equation}
T_{\alpha\beta} = \frac{\partial^2\phi}{\partial x_{\alpha}\partial x_{\beta}}
\end{equation}
%.........................................................................
where the physical gravitational potential has been rescaled by a factor 
$4\pi G\bar{\rho}$ in such a way that $\phi$ satisfies the following 
equation

%.........................................................................
%Poisson
\begin{equation}
\nabla^2\phi = \delta,
\end{equation}
%.........................................................................
with $\bar{\rho}$ the average density in the Universe, $G$ the 
gravitational constant and $\delta$ the dimensionless matter overdensity.

Since the tidal tensor can be represented in any cell by a real and 
symmetric $3\times 3$ matrix, it is ensured the possibility to diagonalize 
it and obtain three real eigenvalues $\lambda_{1} > \lambda_{2}>\lambda_3$.
This set of eigenvalues can be used as indicators of the local orbital 
stability in each proper direction, which in turn can be translated into 
a classification scheme of the Cosmic Web. A counting of the number of 
positive (stable) or negative (unstable) eigenvalues allows to catalogue
a single cell into one of the next four types of environment: voids (3 
negatives eigenvalues), sheets (2), filaments (1) and knots (0). A 
significant improvement to this scheme was introduced by \citet{Forero09}
by means of a relaxation of the stability criterion. The relative strength 
of each eigenvalue is no longer defined by the sign, but instead by a
threshold value $\lambda_{th}$ which can be tuned in such a way that the
visual impression of the web-like matter distribution is reproduced.

%-------------------------------------------------------------------------
\subsection{The velocity  web (V-web)}
\label{subsec:Vweb}
%-------------------------------------------------------------------------

We also use a kinematical method to define the cosmic-web environment in 
the simulation. The method has been thoroughly described in XXX and 
applied to study the shape and spin alignment in the Bolshoi simulation 
here XX. We refer the reader to these papers to find a detailed 
description of the algorithm, its limitations and capabilities. Here we 
summarize the most relevant points for the discussion.

The V-web method for environment finding is based on the local shear 
tensor calculated from the smoothed DM velocity field in the simulation.
The central quantity is the following dimensionless quantity

%.........................................................................
%V-Web Definition
\eq{V_web}
{
\Sigma_{\alpha\beta} = -\frac{1}{2H_0}\pr{\frac{\partial v_{\alpha}}
{\partial x_{\beta}}+\frac{\partial v_{\beta}}{\partial x_{\alpha}}}
}
%.........................................................................
where $v_{\alpha}$ and $x_{\alpha}$ represent the $\alpha$ component of 
the comoving velocity and position, respectively. $\Sigma_{\alpha\beta}$ 
can be represented by a $3\times 3$ symmetric matrix with real values,
that ensures that is possible to diagonalize and obtain three real 
eigenvalues $\lambda_{1} > \lambda_{2}>\lambda_3$ whose sum (the trace of
$\Sigma_{\alpha\beta}$) is proportional to the divergence of the local 
velocity field smoothed on the physical scale ${\mathcal R}$.

The relative strength of the three eigenvalues with respect to a threshold
value $\lambda_{th}$ allows for the local classification of the matter 
distribution into four web types: voids, sheets, filaments and peaks, 
which correspond to regions with 3, 2, 1 or 0 eigenvalues with values 
larger than $\lambda_{th}$. Below we shall discuss a novel approach to 
define an adequate threshold value based on the visual impression of void
regions, furthermore we study other possible values based on other visual
features of the cosmic web.

@@

%.........................................................................
%Table of sizes of each sample defined in Bolshoi
\begin{table}[h]
\begin{flushleft}
\begin{center}
  \begin{tabular}{l  r  r  r r} \hline\hline
	\textbf{volume}					&				&\textbf{scheme}& \\
	\textbf{fraction}				&\textbf{T-web}	&\textbf{V-web}	&	\textbf{Density}  &  $\bf{\delta_{th}}$  \\ \hline
	Voids							&	$54.88\%$	&	$47.06\%$	&	$50.97\%$	&	$ -0.57$			\\ 
	Sheets							&	$33.21\%$	&	$39.54\%$	&	$36.38\%$ 	&	$0.60$				\\
	Filaments						&	$11.16\%$	&	$12.18\%$	&	$11.67\%$ 	&	$8.82$				\\
	Knots							&	$0.75\%$	&	$1.22\%$	&	$0.98\%$  	&	--		\\ \hline\hline
  \end{tabular}  
  \captionof{table}{\small Size of each sample defined in the Bolshoi 
  simulation and for each of the two schemes used to detect halos (FOF 
  and BDM).}

  \label{tab:Samples_Size}

\end{center}
\end{flushleft}
\end{table}
%.........................................................................

%.........................................................................
%FIGURE 1: Distributions of FA and density regarding the Lambda_1 eigenvalue
\begin{flushleft}
\begin{figure*}
\centering

  \includegraphics[trim = 2mm 2mm 5mm 6mm, clip, keepaspectratio=true,
  width=0.3\textheight]{./figures/cosmicweb_volume_Tweb.pdf}
  \includegraphics[trim = 2mm 2mm 5mm 6mm, clip, keepaspectratio=true,
  width=0.3\textheight]{./figures/cosmicweb_volume_Vweb.pdf}

@@

@@

>>>>

%-------------------------------------------------------------------------
\subsection{The tidal web finder (T-web)}
\label{subsec:Tweb}
%-------------------------------------------------------------------------

This scheme was initially proposed by \citet{Hahn07} as a novel 
alternative for classifying the Cosmic Web based on the tidal tensor, 
that is somehow more fundamental than the density field as it also allows 
to quantify the orbital dynamics of the matter field. This approach is 
reached by a second-order expansion of the equations of motion around 
local minima of the gravitational potential and then extended to any 
position. The second-order term corresponds to the tidal tensor, which is 
defined as the Hessian of the normalized gravitational potential

%.........................................................................
%Tidal Tensor
\eq{V_web}
{	T_{\alpha\beta} = \frac{\partial^2\phi}{\partial x_{\alpha}\partial x_{\beta}}	}
%.........................................................................
where the physical gravitational potential has been rescaled by a factor 
$4\pi G\bar{\rho}$ in such a way that $\phi$ satisfies the following 
equation

%.........................................................................
%Poisson
\eq{Poisson}
{	\nabla^2\phi = \delta,	}
%.........................................................................
with $\bar{\rho}$ the average density in the Universe, $G$ the 
gravitational constant and $\delta$ the dimensionless matter overdensity.

Since the tidal tensor can be represented in any cell by a real and 
symmetric $3\times 3$ matrix, it is ensured the possibility to diagonalize 
it and obtain three real eigenvalues $\lambda_{1}\geq\lambda_{2}\geq
\lambda_3$. This set of eigenvalues can be used as indicators of the local 
orbital stability in each proper direction, which in turn can be 
translated into a classification scheme of the Cosmic Web. A counting of 
the number of positive (stable) or negative (unstable) eigenvalues allows 
to catalogue a single cell into one of the next four types of environment: 
voids (3 negatives eigenvalues), sheets (2), filaments (1) and knots (0). 
A significant improvement to this scheme was introduced by \citet{Forero09}
by means of a relaxation of the stability criterion. The relative strength 
of each eigenvalue is no longer defined by the sign, but instead by a
threshold value $\lambda_{th}$ that can be tuned in such a way that the
visual impression of the web-like matter distribution is reproduced.

%-------------------------------------------------------------------------
\subsection{The velocity web finder (V-web)}
\label{subsec:Vweb}
%-------------------------------------------------------------------------

We also use a kinematical scheme to define the Cosmic Web environment in 
the simulation. The scheme has been thoroughly described in 
\citet{Hoffman12} and applied to study the shape and spin alignment in the
Bolshoi simulation in \citet{Libeskind13}. We refer the reader to these 
papers to find a detailed description of the algorithm, its limitations 
and capabilities. The V-web scheme for environment finding is based on the
local velocity shear tensor calculated from the smoothed dark matter 
velocity field in the simulation. The central quantity is given by the 
following dimensionless expression

%.........................................................................
%V-Web Definition
\eq{V_web}
{	\Sigma_{\alpha\beta} = -\frac{1}{2H_0}\pr{\frac{\partial v_{\alpha}}
{\partial x_{\beta}}+\frac{\partial v_{\beta}}{\partial x_{\alpha}}}	}
%.........................................................................
where $v_{\alpha}$ and $x_{\alpha}$ represent the $\alpha$ component of 
the comoving velocity and position, respectively. Like the tidal tensor, 
$\Sigma_{\alpha\beta}$ can be represented by a $3\times 3$ symmetric 
matrix with real values, hence diagonalizing it is obtained three real 
eigenvalues $\lambda_{1}\geq\lambda_{2}\geq\lambda_3$ whose sum (the 
trace of $\Sigma_{\alpha\beta}$) is proportional to the divergence of the 
local velocity field smoothed on the physical scale ${\mathcal R}$.

In the same way, the relative strength of the three eigenvalues with 
respect to a threshold value $\lambda_{th}$ allows for the local 
classification of the matter distribution into the previous four web types. 
For the threshold choosing in both schemes, the V-web and the T-web, it is
usual to fine-tuning the value in such a way that the visual appearance of
the Cosmic Web as seen in simulations and galaxy surveys is reproduced. 
However, we do not take this approach here, instead we propose a novel 
approach for the threshold choosing based on the maximization of the 
fractional anisotropy field occurring in filaments and very dense walls.

%.........................................................................
%FIGURE 1: Distributions of FA and density regarding the Lambda_1 eigenvalue
\begin{flushleft}
\begin{figure*}
\centering
  \includegraphics[trim = 2mm 2mm 5mm 6mm, clip, keepaspectratio=true,
  width=0.3\textheight]{./figures/cosmicweb_volume_Tweb.pdf}
  \includegraphics[trim = 2mm 2mm 5mm 6mm, clip, keepaspectratio=true,
  width=0.3\textheight]{./figures/cosmicweb_volume_Vweb.pdf}

  \label{fig:VFF}
  \vspace{0.1 cm}

  \captionof{figure}{\small Distribution of the fractional anisotropy 
  (upper panel) and density field (lower panel) with respect to the 
  eigenvalue $\lambda_1$ for each web scheme (T-web, red lines. V-web, 
  blue lines) as calculated over all the cells of the grid. Thick central 
  lines correspond to the median of the distribution and coloured regions 
  to the $50\%$ of the cells, delimited by quartiles $Q_1$ and $Q_3$.}

%-------------------------------------------------------------------------
\subsection{Density-based web finder}
\label{subsec:Vweb}
%-------------------------------------------------------------------------

In order to compare our tracing field based on the fractional anisotropy,
we define here a very basic approach for environmental finding based on 
three thresholds set in the density field. Although the density field is
a key quantity for understanding the large-scale Universe, the filamentary 
structure of the Cosmic Web is poorly traced by it (see figure 
\ref{fig:FA_field}).

%.........................................................................
%Table with volume filling fraction
\begin{table}[h]
\begin{flushleft}
\begin{center}
  \begin{tabular}{c  c  c  c c} \hline\hline
	\textbf{Volume}					&				&\textbf{Scheme}& \\
	\textbf{Filling}				&				&				&					  &  \textbf{Threshold} \\ 
	\textbf{Fraction}				&\textbf{T-web}	&\textbf{V-web}	&	\textbf{Density}  &  $\bf{\delta_{th}}$  \\ \hline
	Voids							&	$54.88\%$	&	$47.06\%$	&	$50.97\%$	&	$ -0.57$			\\ 
	Sheets							&	$33.21\%$	&	$39.54\%$	&	$36.38\%$ 	&	$0.60$				\\
	Filaments						&	$11.16\%$	&	$12.18\%$	&	$11.67\%$ 	&	$8.82$				\\
	Knots							&	$0.75\%$	&	$1.22\%$	&	$0.98\%$  	&	--		\\ \hline\hline
  \end{tabular}  
  \captionof{table}{\small Size of each sample defined in the Bolshoi 
  simulation and for each of the two schemes used to detect halos (FOF 
  and BDM).}

  \label{tab:VFF}
\end{center}
\end{flushleft}
\end{table}
%.........................................................................

@@

@@

  \label{fig:volume_function}
  \vspace{0.1 cm}

@@

  \label{fig:shape_distro}
  \vspace{0.1 cm}
